### 2016-06-29 GPCE2016/sections/Introduction.tex
author-info & revise.

This paper presents a third alternative: the concept of
\emph{\interfacebased} \objectoriented programming languages (IB), where objects
implement interfaces directly. In IB interfaces own the implementation
for the behaviour, which is structurally defined in their
interface. Programmers do not define objects directly, but delegate
the task to \emph{object interfaces}, whose role is similar to non-abstract
classes in \classbased \objectoriented programming languages
(CB). Objects 
are instantiated by static factory methods in object interfaces.

@@

Object interfaces
provide support for automatic type-refinement.
In contrast, in CB 
special care and verbose explicit type-refinement is be required to
produce code that deals with subtyping adequately.

  We believe that such verbosity hindered and slowed
down the discovery of useful programming patterns involving
type-refinement. A recently discovered
solution~\cite{eptrivially} to the Expression
Problem~\cite{wadler98expression} in Java-like languages, shows how easy it is to solve
the problem using only type-refinement. However it took nearly 20
years since the formulation of the problem for that
solution to be presented in the literature. In IB, due to
its emphasis on type-refinement, that solution should have been much
more obvious.

>>>>

This paper presents a third alternative: the concept of
\emph{\interfacebased} \objectoriented programming languages (IB), where objects
implement interfaces directly. In IB interfaces own the implementation
for the behaviour, which is structurally defined in their
interface. Programmers do not define objects directly but delegate
the task to \emph{object interfaces}, whose role is similar to non-abstract
classes in \classbased \objectoriented programming languages
(CB). Objects 
are instantiated by static factory methods in object interfaces.

@@

Object interfaces
provide support for automatic type-refinement.
In contrast, in CB 
special care and verbose explicit type-refinement are required to
produce code that deals with subtyping adequately.

We believe that such verbosity hindered and slowed
down the discovery of useful programming patterns involving
type-refinement. A recently discovered
solution~\cite{eptrivially} to the Expression
Problem~\cite{wadler98expression} in Java-like languages shows how easy it is to solve
the problem using only type-refinement. However it took nearly 20
years since the formulation of the problem for that
solution to be presented in the literature. In IB, due to
its emphasis on type-refinement, that solution should have been much
more obvious.
